Self Regulation Ontology Retest Data: Meaningful Variables Clean

### 2017-03-09 SRO_Meaningful_Vars.Rmd
Organizing shorter nb

```{r echo=TRUE}
rm(i)
```

@@

solution <- fa(r = corMat, nfactors = 3, rotate = "oblimin", fm = "pa")
```

@@

>>>>

```{r echo=FALSE}
rm(i)
```

@@

solution <- fa(r = corMat, nfactors = 7, rotate = "oblimin", fm = "pa")
```

@@

```{r}
# Pricipal Components Analysis
# entering raw data and extracting PCs 
# from the correlation matrix 
fit <- principal(rest_subs_test_mngf_z, nfactors=7, rotate="varimax")
fit

fit <- princomp(rest_subs_test_mngf_z, cor=TRUE)
summary(fit) # print variance accounted for 
loadings(fit) # pc loadings 
plot(fit,type="lines") # scree plot 
fit$scores # the principal components
biplot(fit)
```
